\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{array}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{booktabs}
\usepackage{charter}
\usepackage{multicol}  

% Colors
\definecolor{bluecolor}{RGB}{40, 80, 150}
\definecolor{graycolor}{RGB}{100, 100, 100}

% Formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\usepackage{setspace}
\setstretch{1.1} 
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\large\bfseries\color{bluecolor}}{}{0pt}{}
\titlespacing{\section}{0pt}{6pt}{3pt}

% Compact lists
\setlist[itemize]{leftmargin=*, nosep, topsep=2pt, partopsep=0pt}
\setlist[enumerate]{leftmargin=*, nosep, topsep=2pt, partopsep=0pt}

% Custom commands
\newcommand{\contacticon}[1]{\raisebox{-0.2ex}{\faIcon{#1}}}
\newcommand{\link}[2]{\href{#1}{\color{bluecolor}#2}}
\newcommand{\datedentry}[2]{\textbf{#1} \hfill #2\\}
\newcommand{\location}[1]{\textit{#1}}

\begin{document}
\fontsize{10}{13}\selectfont 

% HEADER
\begin{center}
    {\Huge \textbf{Md Safwan Bin Rashid}} \\[6pt]
    {\small 
        \contacticon{map-marker-alt} 105 Ross Blvd, Apt C8, Hattiesburg, MS 39401 \quad 
        \contacticon{mobile-alt} (601) 913-8400 \\[2pt]
        \contacticon{envelope} \href{mailto:mdsafwanbin.rashid@usm.edu}{MdSafwanBin.Rashid@usm.edu} \quad 
        \contacticon{linkedin} \href{http://www.linkedin.com/in/md-safwan-bin-rashid-887439249}{LinkedIn} \quad 
        \contacticon{github} \href{https://github.com/MdSafwanBinRashid}{GitHub}
    }
\end{center}

\vspace{2pt}

% EDUCATION
\section*{Education}\vspace{-2pt}\hrule\vspace{6pt}
\textit{The University of Southern Mississippi} \hfill Aug 2024 -- May 2028\\
\textbf{B.S. in Computer Science, Minor in Psychology} \hfill CGPA: 3.91\\
\textbf{Relevant Coursework:} Database Management, Software Dev. Foundations, Data Structures and Algorithms, Calculus w/ Analytical Geometry, Statistics for Behavioral Sciences, Cyber Law and Ethics, Info Tech Project Management

% RESEARCH EXPERIENCE
\section*{Research Experience}\vspace{-2pt}\hrule\vspace{6pt}
\begin{tabular}{@{}p{0.17\textwidth} p{0.77\textwidth}@{}}
\textbf{} & \textbf{Undergraduate Research Assistant,} Uof Southern Mississippi \\[1em]

\textbf{Feb 2026 -- Present} & \textbf{Virtual Reality Lab}, School of Computing Sciences and Computer Engineering \\[0.2em]
\textbf{} & \textit{Supervised by Dr. Partha Sengupta} \\[0.5em]
\textbf{} & Working on a bifurcated project titled “VR Teaching for K-12 Students and Creating Human Resources for Agricultural Applications.” \\[2.5em]

\textbf{Jul 2025 -- Present} & \textbf{Experimental Health Psychology Lab}, School of Psychology \\[0.2em]
\textbf{} & \textit{Supervised by Dr. Tammy Greer} \\[0.5em]
& 
\begin{minipage}[t]{0.9\linewidth}
\begin{itemize}
    \item Co-author manuscripts; conduct statistical analysis using SPSS
    \item Conceptualize and lead a study on “Acculturation through AI Interventions”
    \item Presented findings at two regional conferences
\end{itemize}
\end{minipage} \\[3em]
\end{tabular}

% SELECTED ONGOING RESEARCH PROJECTS
\section*{Selected Ongoing Research Projects}\vspace{-2pt}\hrule\vspace{6pt}

\begin{itemize}
    \item Stimulating Belonging Through AI To Address Imposter Syndrome and Enhance Cultural Integration Among International Students
    \item Locus of Control in the Virtual World: How Online Harassment Influences Consumption Behaviors
    \item Screen Time, Attention Control, Stress, and Social Functioning: The Psychological Correlates of Smartphone Dependency in College Students
    \item Dual Burden of Digital Dependency: Night Eating Syndrome and Body Dissatisfaction
    \item Loneliness as a Moderator: Demographic Differences in Sugar-Sweetened Beverage (SSBs) and Mental Health
\end{itemize}

% CONFERENCE PRESENTATIONS
\section*{Conference Presentations}\vspace{-2pt}\hrule\vspace{6pt}
\begin{itemize}
    \item Akter, K., Greer, T., Slay, M., Mahjabin, N., Bainer, E., \textbf{Rashid, M. S.} (2026, March). Eating and drinking during emotional distress: How coping styles shape sugar-sweetened beverage (SSB) consumption and emotional eating. 90th Annual Meeting of the Mississippi Academy of Sciences, Biloxi, MS.
    
    \item Akter, K., Greer, T., Slay, M., Mahjabin, N., \textbf{Rashid, M. S.}, Ahmed, I. (2026, March). Gynecological Health Disparities and Mental Health Outcomes Among Minority Women. 72nd Annual Meeting, Southeastern Psychological Association, New Orleans, LA.
\end{itemize}

% TECHNICAL PROJECTS
\section*{Technical Projects}\vspace{-2pt}\hrule\vspace{6pt}
\begin{itemize}[label=\raisebox{0.25ex}{\rule{0.7ex}{0.7ex}}]

    \item \textbf{PyTorch Tabular Data Classification} \textit{(Pilot Project)}
    \faIcon{github}\link{https://github.com/MdSafwanBinRashid/ML_DL_Pilots/blob/main/PyTorch_Tabular_Data_Classification.ipynb}{[Github]}
    \begin{itemize}[label=--, nosep]
        \item Built and trained a feedforward neural network in PyTorch to classify rice grain types from physical measurements.
    \end{itemize}

    \vspace{8pt}
    
    \item \textbf{EEG Signal Processing} \textit{(Pilot Project)}
    \faIcon{github}\link{https://github.com/MdSafwanBinRashid/Electroencephalography/blob/main/EEG_Signal_Processing.ipynb}{[Github]}
    \begin{itemize}[label=--, nosep]
        \item Built an MNE-Python pipeline to preprocess raw EEG data, including filtering, epoching, and artifact rejection.
        \item Extracted and visualized P300 event-related potentials (ERPs) across stimulus conditions.
    \end{itemize}

    \vspace{8pt}
    
    \item \textbf{AVL Student Database} \textit{(DSA307)} 
    \faIcon{github}\link{https://github.com/MdSafwanBinRashid/AVLStudentDB}{[Github]}
    \begin{itemize}[label=--, nosep]
        \item Implemented a self-balancing AVL tree in C++ to manage records with O(log n) operations.
        \item Integrated CSV file I/O for persistent data storage between sessions.
    \end{itemize}

    \vspace{8pt}
    
    \item \textbf{Alumni Networking Platform V1.0} \textit{(ITC371)} 
    \begin{itemize}[label=--, nosep]
        \item Developed a complete project plan including scope definition, WBS, risk assessment, and resource allocation.
        \item Designed system architecture and stakeholder communication protocols for university alumni networking.
    \end{itemize}
    
    \vspace{8pt}
    
    \item \textbf{Immutable Criminal Record Keeping with Blockchain} \textit{(BCOLBD '23)}
    \begin{itemize}[label=--, nosep]
        \item Co-authored whitepaper and presented poster on Hyperledger Fabric-based secure evidence management system.
        \item Represented Team Genesis in National Blockchain Competition.
    \end{itemize}
\end{itemize}

% AWARDS & ACHIEVEMENTS
\section*{Awards \& Achievements}\vspace{-2pt}\hrule\vspace{6pt}
\begin{itemize}
    \item {President's List} (Fall '25) | School of CSCE
    \item {Dean's List} (Fall '24, Spring '25) | School of CSCE
    \item Academic Excellence Scholar '23 (4 years)
    \item Semi-finalist | ClimateScience Olympiad '23
    \item {Valedictorian} (Class of '22) | Willes Little Flower School \& College
    \item Head Boy (Letter of Commendation) | Willes Little Flower School \& College
\end{itemize}

% SKILLS
\section*{Skills}\vspace{-2pt}\hrule\vspace{6pt}
\begin{itemize}[label=$\circ$]
    \item \textbf{Programming Languages:} C, C++, Python
    \item \textbf{Database:} MySQL
    \item \textbf{Machine Learning:} PyTorch, Scikit-learn, NumPy, Pandas, Matplotlib, Seaborn
    \item \textbf{IDE:} Colab, Jupyter Notebook, VSCode, PyCharm, Xcode, Code::Blocks
    \item \textbf{SWE:} Git, HTML5, CSS3, JavaScript
    \item \textbf{Research:} Qualtrics, IBM SPSS
    \item \textbf{Others:} Competitive Programming, AutoCAD
\end{itemize}

% JOB EXPERIENCE
\section*{Job Experience}\vspace{-2pt}\hrule\vspace{6pt}
\begin{tabular}{@{}p{0.18\textwidth} p{0.9\textwidth}@{}}

\textbf{Aug 2024 -- Present} & \textbf{Campus Dining Crew, } Aramark Campus LLC, Hattiesburg, MS \\[0.3em]
& Managing cafeteria operations; assisting with catering for campus events.\\[1em]

\textbf{Jul 2022 -- Jun 2023} & \textbf{Junior Executive, } Energypac Power Generation PLC, Dhaka, BD \\[0.3em]
& 
\begin{minipage}[t]{0.9\linewidth}
\begin{itemize}
    \item Secured a year-long role at Energypac, a leading power engineering firm in Bangladesh
    \item Managed FIFO inventory system
    \item Optimized logistics plans to streamline supply chain operations for large-scale projects
\end{itemize}
\end{minipage} \\[1em]

\end{tabular}

% INVOLVEMENT
\section*{Involvements}\vspace{-2pt}\hrule\vspace{6pt}
\begin{itemize}
    \item \textbf{Chapter Member} | Psi Chi International Honor Society in Psychology \hfill Apr 2026 -- Present
    \item \textbf{Event Coordinator} | Bangladeshi Student Association (BSA) \hfill Aug 2024 -- May 2025
    \item \textbf{Volunteer} | Purnota Foundation \hfill Feb 2024 -- Present
    \item \textbf{French Instructor} | DPT Foreign Language Club | DP Tutorials \hfill Jun 2023 -- Mar 2024
\end{itemize}

% LANGUAGE
\section*{Language}\vspace{-2pt}\hrule\vspace{6pt}
English (C2), French (B1), Urdu (B1), Bengali (Native)

% REFERENCES
\section*{References}\vspace{-2pt}\hrule\vspace{6pt}

\noindent
\begin{minipage}[t]{0.45\textwidth}
    \textbf{Dr. Partha Sengupta} \\
    Assistant Professor \\
    School of Computing Sciences and \\
    Computer Engineering \\
    The University of Southern Mississippi \\
    Contact: \href{mailto:Partha.Sengupta@usm.edu}{Partha.Sengupta@usm.edu}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
    \textbf{Dr. Tammy Greer} \\
    Associate Professor \\
    School of Psychology \\
    The University of Southern Mississippi \\
    Contact: \href{mailto:Tammy.Greer@usm.edu}{Tammy.Greer@usm.edu}
\end{minipage} \\

\noindent\textit{More References available upon request.}

\end{document}
